\pdftitle

### 2017-05-16 maxNt.tex
adding a short introduction on the usage of MaxEnt in neuroscence

The \me\ method is used in neuroscience blahblah***

\mynote{Version 1}
The present note has three nested purposes.

>>>>

Recent advances in electrophysiological recordings allow to
 study the collective behavior of large population of neurons 
in relation to stimuli and bahavioral tasks [\cite]. Huge amount of parallel
 recordings from hundreds of neurons, available today, is accompanied by
 the statistical challenges to shed light on the mechanism behind neuronal coding. 
The principle of \me\ was proposed as a way to overcome these challenges by constructing a full description of the 
neuronal firing patterns based on only first and second order statistics of the observed data [\cite].

 used in neuroscience to study the patterns of neuronal
 firing in relation to stimuli or behavioral tasks. These studies strive for understanding the 
mechanism behind neuronal coding. 
 by answering
 questions such as, which level of interaction (pairwise or higher-order) between neurons
 is suffiecient to explain the observed experimental data [\cite]? Or how collective behavior
 of neurons can be related to stimuli or behavioral tasks [\cite]? These questions 
**********
\mynote{Version 1}
The present note has three nested purposes.
